25 years of Social Work Research

### 2015-04-02 dataCleaning.Rmd
Updated Tableau charts.

```{r eval=TRUE}
# Read data files
#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
#countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")

# Load special functions
#source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")

source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")

@@

```{r locationExtraction2, eval=TRUE}
LO.df2 <- filter(full.df, attributes == "abstract" |
                 attributes == "article" | attributes == "keyword")
indx.country <- paste(countries.csv$x, collapse = "[\\s|[[:punct:]]]|")
library(stringi)
countries.extracted <- na.omit(within(LO.df2, text1<- stri_extract(LO.df2$record, opts_fixed=TRUE, regex=indx.country)))[-2]
countries.extracted$text1<-gsub("[[:punct:]]", "", countries.extracted$text1)
countries.extracted$text1<-gsub("^\\s+|\\s+$", "", countries.extracted$text1)

@@

detach(package:stringi)

@@

@@

```{r pages, eval=TRUE}
pages.df <- full.df %>% filter(attributes == "pages")
page.identifier <- grepl("[-p]", pages.df$record)
pages.df.reduced <- pages.df[page.identifier == FALSE,]

reduced <- full.df[full.df$articleID %in% pages.df.reduced$articleID, ]
reduced <- filter(reduced, attributes == "article" | attributes == "journal" | 
            attributes == "pubYear" | attributes == "pages" | attributes == "abstract")

>>>>

```{r eval=TRUE}
# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
#countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")

# Load special functions
source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")

#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")

@@

```{r locationExtraction2, eval=TRUE}
LO.df2 <- filter(full.df, attributes == "abstract" |
                 attributes == "article" | attributes == "keyword")
indx.country <- paste(countries.csv$x, collapse = "[\\s|[[:punct:]]]|")

library(stringi)
countries.extracted <- na.omit(within(LO.df2, text1 <- stri_extract(LO.df2$record, regex=indx.country)))[-2]
countries.extracted$text1<-gsub("[[:punct:]]", "", countries.extracted$text1)
countries.extracted$text1<-gsub("^\\s+|\\s+$", "", countries.extracted$text1)

@@

#detach(package:stringi)

@@

```{r gade, eval=TRUE}

years <- c(1989:2015)
programs <- rep(NA, 27)
gade <- as.data.frame(cbind(as.character(years), programs))
gade$programs <- as.numeric(gade$programs)
gade[15, 2] <- 72
gade[27, 2] <- 86
colnames(gade) <- c("years", "programs")
```

```{r pages, eval=TRUE}
pages.tmp <- full.df %>% filter(attributes == "pages")
years.tmp <- full.df %>% filter(attributes == "pubYear")
pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
    select(record.y, record.x) %>%
    rename(years = record.y, pages = record.x) %>%
    mutate(pages = as.numeric(pages)) %>%
    group_by(years) %>%
    summarise(
        Median.Pages = median(pages, na.rm=TRUE), 
        Mean.Pages = mean(pages, na.rm=TRUE),
        Std.Pages = sd(pages, na.rm=TRUE))

@@

```{r}
colnames(n.journals.year) <- c("years", "journals")
n_authors2 <- rename(n_authors2, years = ID, Avg.Authors = Average, Mdn.Authors = Median, Sd.Authors = Standard_Deviation)

scholarly.df <- left_join(articles.year.df, n.journals.year, by = "years") 
scholarly.df <- left_join(scholarly.df, n_authors2, by = "years")
scholarly.df <- left_join(scholarly.df, nsf, by = "years")
scholarly.df <- left_join(scholarly.df, pages.df, by = "years")
scholarly.df[c(26, 27), ] <- rep(NA)
scholarly.df[26, 1] <- 2014
scholarly.df[27, 1] <- 2015

scholarly.df <- mutate(scholarly.df, years = as.numeric(years)) %>%
    rename(article.count = year.count, journal.count = year.count, program.growth = growth) 
scholarly.df$gade <- rep(NA, nrow(scholarly.df))  
scholarly.df$gade[15] <- 72
scholarly.df$gade[27] <- 86

write.csv(scholarly.df, file = "scholarship.csv")
